# Load the data
```{r}
data <-
  readRDS(here::here("Data/water_energy_MW.rds")) %>%
  .[, me := water_est - volaf] %>%
  .[me < 200, ]
```

# Map

```{r}
data %>%
  unique(by = "wellid") %>%
  sf::st_as_sf(coords = c("longdd", "latdd"), crs = 4269) %>%
  ggplot(data = .) +
  geom_sf()
```

# Water vs Energy

```{r}
w_e_reg <-
  data %>%
  nest_by(nrdname) %>%
  dplyr::filter(nrdname != "Twin Platte") %>%
  dplyr::mutate(reg_ga = list(
    mgcv::gam(volaf ~ s(kwh), data = data)
  ))
```

## Middle
```{r}
w_e_reg$reg[[1]] %>% plot()
```

## Upper

```{r}
w_e_reg$reg[[2]] %>% plot()
```

Both linear. 

## Yearly energy use efficiency by NRD

Significant difference in energy use efficiency between URNRD and MRNRD. What are potential causes?

+ depth to water table
+ pumping efficiency
+ water use

```{r}
data[nrdname != "Twin Platte", ] %>%
  .[kwh != 0, ] %>%
  .[, mean(volaf / kwh, na.rm = TRUE), by = .(year, nrdname)]
```

Not sure what is going on in 2008.

# Measurement error 

Water use was estimated based on enegy use by multyplying energy use with a single coefficient to all the data.

## Yearly measurement errors 


```{r}
data[nrdname != "Twin Platte", ] %>%
  .[me < 200, ] %>%
  ggplot(data = .) +
  geom_point(aes(y = volaf, x = water_est), size = 0.1) +
  geom_smooth(aes(y = volaf, x = water_est), size = 0.1, method = "lm") +
  facet_grid(nrdname ~ year) +
  geom_abline(intercept = 0, slope = 1) +
  xlab("Water Use Estimates Based on Energy Use (acre-feet)") +
  ylab("Observed Water Use (acre-feet)") +
  theme_bw() +
  theme(legend.position = "bottom") +
  coord_equal() +
  scale_x_continuous(breaks = (1:9) * 100) +
  scale_y_continuous(breaks = (1:9) * 100)
```

You can observe that water use tend to be overestimated for high-water use observations.

## Yearly ME (histogram)

```{r}
data[nrdname != "Twin Platte", ] %>%
  .[, me := water_est - volaf] %>%
  .[me < 250, ] %>%
  ggplot(data = .) +
  geom_histogram(aes(x = me)) +
  geom_vline(xintercept = 0, color = "red") +
  facet_grid(year ~ nrdname)
```

